### 2023-12-12 main.tex
''

		means that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {\color{blue} at sites $q_{k}$ for $k=1,\ldots,b$ we have a particle of type $a_{k}$, while at the other sites the occupation $\tau_{x}$ is left unchanged  ($x\notin\{q_{1},\ldots,q_{b}\}$). } 
		\todo{mention also fat $\bm{\tau}$ in this sentence somehow.}

>>>>

		means that, {\color{blue} given $\bm{\tau}$ from the bra-vector $\langle \bm{\tau}|$ introduced before equation \eqref{Tensor-S1},} for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$ {\color{blue} at sites $q_{k}$ (for $k=1,\ldots,b$) we have a particle of type $a_{k}$, while at the other sites the occupation $\tau_{x}$ is left unchanged  ($x\notin\{q_{1},\ldots,q_{b}\}$). } 
		\todo{mention also fat $\bm{\tau}$ in this sentence somehow.[DONE]}
